International impact of large multi-centre surgical trials of arthroscopic subacromial decompression

### 2021-11-17 Paper-ASAD-rates.Rmd
Update strobe and add line numbers (previous commit used for v1 preprint)

---
title: "International impact of large multi-centre surgical trials of arthroscopic subacromial decompression"
output:
  bookdown::pdf_document2: 
    keep_tex: no
    toc: false
    number_sections: false
  bookdown::word_document2:
    toc: false
    reference_docx: paper/my_style.docx
    number_sections: false
  bookdown::html_document2:
    toc: false
bibliography: Paper/references.bib
csl: Paper/bmj.csl
---

>>>>

---
title: "International impact of large multi-centre surgical trials of arthroscopic subacromial decompression"
header-includes:
   - \usepackage{lineno}
   - \linenumbers
output:
  bookdown::word_document2:
    toc: false
    reference_docx: paper/my_style.docx
    number_sections: false
  bookdown::pdf_document2: 
    keep_tex: no
    toc: false
    number_sections: false
  bookdown::html_document2:
    toc: false
bibliography: Paper/references.bib
csl: Paper/bmj.csl
---
